Linting Linearity in Core/System FC

### 2023-09-12 language-v4/proofs/optimizations/BetaReduction.tex
Mre typesetting proofs
Improve assumptions, finish beta reduction

\begin{tabbing}
    Subcase $\pi = 1,p$\\
    (1) $\G,\G' \vdash (\lambda \x[1,p][\s].~e)~e' : \vp$\\
    (2) $\G \vdash (\lambda \x[1,p][\s].~e) : \s \to_{1,p} \vp$\` by inv. on $\lambda E_{1,p}$\\
    (3) $\G' \vdash e' : \s$ \` by inv. on $\lambda E_{1,p}$\\
    (4) $\G,\x[1,p][\s] \vdash e : \vp $\`by inv. on $\lambda I$\\
    (5) $\x[1,p][\s] \notin \G$\`by inv. on $\lambda I$\\
    (6) $\G,\G' \vdash e[e'/x] : \vp$\` by lin. subst. lemma (4,3) and (5)\\
    Subcase $\pi = \omega$\\
    (1) $\G,\G' \vdash (\lambda \xo.~e)~e' : \vp$\\
    (2) $\G \vdash (\lambda \xo.~e) : \s \to_\omega \vp$\` by inv. on $\lambda E_\omega$\\
    (3) $\G' \vdash e' : \s$ \` by inv. on $\lambda E_\omega$\\
    (4) $\hasnolinearvars{\G'}$ \` by inv. on $\lambda E_\omega$\\
    (5) $\G,\xo \vdash e : \vp$\` by inv. on $\lambda I$\\
    (6) $\xo \notin \G$\` by inv. on $\lambda I$\\
    (7) $\G,\G' \vdash e[e'/x] : \vp$\` by unr. subst. lemma (5,3,4)\\
\end{tabbing}
\end{proof}

@@

\begin{tabbing}
    (1) $\G,\G' \vdash (\lambda \xo.~e)~e' : \vp$\\
    (2) $\G \vdash (\lambda \xo.~e) : \s \to_\omega \vp$\` by inv. on $\lambda E_\omega$\\
    (3) $\G', \cdot \vdash e' : \s$ \` by inv. on $\lambda E_\omega$\\
    (4) $\hasnolinearvars{\G'}$ \` by inv. on $\lambda E_\omega$\\
    (5) $\G,\xo \vdash e : \vp$\` by inv. on $\lambda I$\\
    (6) $\G, \cdot, \x[\cdot][\s] \vdash e : \vp$\` by $\xo = \x[\cdot][\s]$ lemma (TODO)\\
    (7) $\G,\G' \vdash \llet{x = e'}{e} : \vp$\` by let (6,3,4)\\
\end{tabbing}
\end{proof}

@@

\begin{proof}
    Trivial through the progress theorem
\end{proof}

>>>>

\begin{tabbing}
% Using preservation
    (1) $\G; \D \vdash (\lambda \xl.~e)~e' : \vp$\\
    (2) $(\lambda \xl.~e) e' \longrightarrow e[e'/x]$\\
    (3) $\G; \D \vdash e[e'/x] : \vp$ \` by type preservation theorem (1,2)\\

% Manually
%    Subcase $\pi = 1,p$\\
%    (1) $\G,\G' \vdash (\lambda \x[1,p][\s].~e)~e' : \vp$\\
%    (2) $\G \vdash (\lambda \x[1,p][\s].~e) : \s \to_{1,p} \vp$\` by inv. on $\lambda E_{1,p}$\\
%    (3) $\G' \vdash e' : \s$ \` by inv. on $\lambda E_{1,p}$\\
%    (4) $\G,\x[1,p][\s] \vdash e : \vp $\`by inv. on $\lambda I$\\
%    (5) $\x[1,p][\s] \notin \G$\`by inv. on $\lambda I$\\
%    (6) $\G,\G' \vdash e[e'/x] : \vp$\` by lin. subst. lemma (4,3) and (5)\\
%    Subcase $\pi = \omega$\\
%    (1) $\G,\G' \vdash (\lambda \xo.~e)~e' : \vp$\\
%    (2) $\G \vdash (\lambda \xo.~e) : \s \to_\omega \vp$\` by inv. on $\lambda E_\omega$\\
%    (3) $\G' \vdash e' : \s$ \` by inv. on $\lambda E_\omega$\\
%    (4) $\hasnolinearvars{\G'}$ \` by inv. on $\lambda E_\omega$\\
%    (5) $\G,\xo \vdash e : \vp$\` by inv. on $\lambda I$\\
%    (6) $\xo \notin \G$\` by inv. on $\lambda I$\\
%    (7) $\G,\G' \vdash e[e'/x] : \vp$\` by unr. subst. lemma (5,3,4)\\
\end{tabbing}
\end{proof}

@@

\begin{tabbing}
    (1) $\G;\D \vdash (\lambda \xo.~e)~e' : \vp$\\
    (2) $\G; \D \vdash (\lambda \xo.~e) : \s \to_\omega \vp$\` by inv. on $\lambda E_\omega$\\
    (3) $\G; \cdot \vdash e' : \s$ \` by inv. on $\lambda E_\omega$\\
    (4) $\G,\xo; \D \vdash e : \vp$\` by inv. on $\lambda I$\\
    (5) $\G, \x[\cdot][\s]; \D \vdash e : \vp$\` by $\xo = \x[\cdot][\s]$ lemma\\
    (6) $\G,\G' \vdash \llet{x = e'}{e} : \vp$\` by let (5,3)\\
\end{tabbing}
\end{proof}

@@

\begin{proof}
    Trivial by invoking preservation using the $\Lambda$ application reduction and the assumption
\end{proof}
